---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# grcard

<!-- badges: start -->
<!-- badges: end -->

The goal of grcard is to created three kinds of dynamic greeting cards - 
    birthday card, Christmas card and "love you" card.

## Installation

You can install the development version of grcard like so:

``` r
install.packages("grcard")
```


## Example

This is a basic example which shows you how to create a GIF card:

```{r example}
library(grcard)
bdcard<-birthday_card(greeting = "Happy birthday my dear friend", color = "strawberry")
bdcard
```

Instead of a GIF card, create a video with music

```{r video}
birthday_video(bdcard)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

