---
title: "grcard package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction of grcard package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(grcard)
```
The "grcard" is package to create greeting cards. The package name "grcard" means "greeting card". At this moment, two kinds of cards could be create with grcard - "Birthday card" and "Christmas card".


This is an attempt of using R to create greeting cards, which I did not see any other packages could do this. It creates dynamic cards in GIF, as well as could generates a video. This is an idea to show the beautiful of data and the romantic of programmers, and just for fun!

Instead of just import images, the greeting cards created with this package are totally based on data. So each kind of cards are having a data set. The data set contains 6 columns, which are "x", "y", "group", "size", "t" and "shape". 

Install packages:
It can be access from the Github: https://github.com/tissuezhang/grcard


## Functions
Six functions are included in this package.


\func{bday_card()} Allows users to create a birthday card in GIF format. 

Usage
bday_card(greeting = "Happy Birthday", color = "cream")

Arguments
greeting	
the greeting words to show on the card

color	
the color of the birthday card, could be choose from "cream", "chocolate" and "strawberry", or create a new color combination by using the \func{bday_color}

Example
```{r}
bday_card(greeting = "Happy birthday my dear friend", color = "chocolate")
```

