---
title: "grcard package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{grcard package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(grcard)
```
The "grcard" is package to create greeting cards. The package name "grcard" means "greeting card". At this moment, two kinds of cards could be create with grcard - "Birthday card" and "Christmas card".


This is an attempt of using R to create greeting cards, which I did not see any other packages could do this. It creates dynamic cards in GIF, as well as could generates a video. This is an idea to show the beautiful of data and the romantic of programmers, and just for fun!

Instead of just import images, the greeting cards created with this package are totally based on data. So each kind of cards are having a data set. The data set contains 6 columns, which are "x", "y", "group", "size", "t" and "shape". 


It can be access from the Github: https://github.com/tissuezhang/grcard

Install packages:
```{r}
devtools::install_github("tissuezhang/grcard")
library(grcard)
```



## Functions
Four functions are included in this package.


\func{bday_card()} Allows users to create a birthday card in GIF format. 

Usage
bday_card(greeting = "Happy Birthday", color = "cream")

Arguments
greeting	
the greeting words to show on the card, default is "Happy Birthday".

color	
the color of the birthday card, could be choose from "cream", "chocolate" and "strawberry".


\func{bday_video()} Allows users to create a birthday card video. The music will created with function automatically, which is the defult of the audio argument. But it also allows users to upload their own mp3 music, as well as change the video's duration and end pause time to match their music duration.

Usage
bday_video(birthdaycard, audio = "bday music.mp3", duration = 13, end_pause = 2)

Arguments
birthdaycard	
the GIF birthday card which created by \func{bday_card()} 

audio	
the audio play with the video, user could upload their own music

duration	
the duration of the video

end_pause	
the pause time at the end


\func{xmas_card()} Allows users to create a Christmas card in GIF format.  Simillar to the \func{bday_card()}.

Usage
xmas_card(greeting = "Merry Christmas", color = "candy")

Arguments
greeting	
the greeting words to show on the card, default is "Merry Christmas".

color	
the color of the Christmas card, could be choose from "forest", "candy" and "dream"

\func{xmas_video()} Allows users to create a Christmas card video. Simillar to the\func{bday_video()} .

Usage
xmas_video(christmascard,audio = "xmas music.mp3",duration = 13, end_pause = 2)

Arguments

christmascard	
the GIF christmas card which created by \func{xmas_card()} 

audio	
the audio play with the video, user could up lode their own music

duration	
the duration of the video

end_pause	
the pause time at the end

# Examples

```{r}
xmas_card(greeting="Marry Christmas my dear friend", color="dream")
```

```{r}
Christmascard<-xmas_card()
xmas_video(Christmascard)
```

# Future Plan

In the future, I would like to create more kinds of cards, such as "thank you", 
"love you", "happy new year","congratulations" and so on...
Also, provide more models for user to choose. For example, different kind of birthday card.
Further more, I would like to create some data set which could plot different elements, such as a "cake", a "gift",or a "flower", and users could create a character card by use these different data set. 
